### 2016-11-03 Hhh/Hhh.tex
Adding more plots and some stats stuff

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{sec:hhh}

In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. This \Pgt-pair final states studied in this analysis
are the \etau, \mutau and \tautau channels. The results of this search are model-independent
upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, which use
combine all three channels. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered. In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau. 
This search will be summarised in this chapter, but will not constitute the main focus.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

@@

A reweighting is applied to make the pile--up distribution in \ac{MC}
match the distribution observed in data.DESCRIPTION

@@

For electrons and muons, these scale factors are measured using a 
tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
The hadronic taus identification, isolation and trigger efficiencies
are measured via a similar method that makes use of
$Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.

FIXME: Tau es?

FIXME: top pt reweighting
FIXME: ttbar scale factor

In the \etau channel a data to \ac{MC} scale factor is applied
to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
fake rate between data and \ac{MC}. DERIVED HOW

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_ttbar.pdf}}
\end{center}
\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $GeV (left) and \ttbar background events (right) in 
the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
accuracy of the mean of the mass distribution in signal events. \cite{HIG-14-034-additional}}%FIXME plots need to be remade as the bkg one was never released
%on the public twiki so can't have the CMS label on
\label{fig:kinfitvsmjj}
\end{figure}

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimated the shape and yield of backgrounds in this analysis, data--driven techniques are
used where possible.

\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.

\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the taus. In this control region
a data-to-\ac{MC} factor is estimated and applied to the yield estimate from \ac{MC}.

\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high \mT to low \mT
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is then the other-background-subtracted
data yield in the high \mT region multiplied by this extrapolation factor.
In the 2jet-2tag, a slightly different high \mT sideband of 60-120 GeV is used 
to give larger statistics for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

The \Wjets shape is taken from the \ac{MC} samples. To 
increase the statistics for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
working point for the purposes of shape estimation.

\subsection{QCD}
\label{sec:hhh_backgrounds_qcd}
A fully data-driven method is used to estimate the QCD background. Data events
passing the signal region selection cuts, but requiring the di-tau pair to be
of the same sign, are used for this. Contributions from other backgrounds are 
subtracted. Because the contribution from opposite- and same-sign QCD are
not exactly the same an OS/SS ratio of 1.06 is measured using data in which
the electron/muon isolation requirement was inverted.

@@

The shapes in all categories are taken from same-sign data with the electron/muon
isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
inverting the light lepton isolation requirements, the category definition
is loosened to obtain the shapes. For the purposes of QCD shape
estimation, jets are considered b-tagged if they pass a looser b-tagging
working point than the working point used elsewhere in the analysis.

\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shape and normalisation are
estimated using \ac{MC} samples.

\section{Systematic uncertainties}
\label{sec:hhh_uncs}
Two types of systematic uncertainties are considered: normalisation
uncertainties (which affect only the yield of a process), and shape
uncertainties (which affect both the yield and shape of a process). Section \ref{sec:hhh_results_extraction}
describes how these uncertainties are taken into account in the final result.

\subsection{Normalisation uncertainties}
\label{sec:hhh_uncs_norm}

\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during
2012 (LUMI POG CITATION?). This uncertainty is applied to all processes in which
the normalisation is estimated using MC samples.

\subsubsection*{Identification, isolation and trigger efficiencies}
A systematic uncertainty due to the uncertainty in efficiency measurements
for the leptons is derived by combining the uncertainties on these measurements
in quadrature. For electrons and muons this leads to a 2\% uncertainty, for hadronic taus a 6\% 
uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3 \% for
the \Pgt legs of the triggers. This uncertainty is applied to all processes for which
the normalisation is estimated using MC samples.

\subsubsection*{$e\rightarrow\Pgt_{h}$ and $\mu\rightarrow\Pgt_{h}$ fake rates}
The uncertainty on both the $e\rightarrow\Pgt$ fake rate measurement and the
$\mu\rightarrow\Pgt$ fake rate measurement is 30\%. The central value of the $\mu\rightarrow\Pgt$
fake rate is close to 1, which is why it is not applied, but the uncertainty is 
taken into account FIXME check if this is true!

\subsubsection*{B-tag scale factors}
The b-tag scale factors are varied within their uncertainties to determine the effect
on the yields of each process. Both a b-tagging uncertainty and a fake mis-tagging
uncertainty are obtained by considering the percentage by which these backgrounds
change when the scale factors are varied within their uncertainty. The b-tagging
efficiency uncertainty amounts to 1-10\% for most processes in most categories, except for the 2jet-2tag
category where a 70\% uncertainty applies to the W background. Due to the nature
of the estimation method, where other backgrounds are subtracted from the data to 
obtain a W estimate, and the presence of large amounts of \ttbar, a 10\% change in the \ttbar
yield can vary the W yield by such large amounts.
The b mistagging rate uncertainty varies between 1-5\% for all processes in all channels.

\subsubsection*{\MET resolution and response}
Uncertainties on the \MET resolution and response are estimated by varying
the recoil correction parameters within their estimated uncertainties. This 
leads to a 1-10\% uncertainty (depending on category and process)

\subsubsection*{Background normalisation}
\begin{itemize}
\item \Ztautau : the normalisation of the embedded samples attracts a 3.3\% uncertainty, which is derived
from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples. In addition an uncertainty of 5-6\% for extrapolation from the inclusive selection to the category selection is applied.
\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\%
\item \ttbar: the uncertainty on the \ttbar cross section is 10\%
\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
\item \Wjets: As the \Wjets yield is estimated from a high \mT sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty range sfrom 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
\item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio. This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category.
\end{itemize}

\subsection{Shape uncertainties}
\label{sec:hhh_uncerts_shape}

\subsubsection*{Tau energy scale}
The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty. As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.

\subsubsection*{Jet energy scale}
The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the (\pT and $\eta$ dependent) uncertainty. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty

\section{\texorpdfstring{Overview of \AtoZhtolltautau}{Overview of A->Zh->lltautau}}
\label{sec:hhh_azh}
In this section a summary of the \AtoZhtolltautau analysis, which is combined with the 
analysis described so far for the purposes of model interpretations, is given.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
\caption{The 95\% confidence level expected (dashed) and observed (solid)
upper limits on the $\sigma \times BR$ for the \AtoZhtolltautau process.
The green and yellow bands indicate the $\pm 1 \sigma $ and $2\sigma$
expectations \cite{CMS-HIG-14-034}.}
\label{fig:AZhUpperLimits}
\end{center}
\end{figure}

More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.

\section{Results}
\label{sec:hhh_results}

\subsection{Signal extraction}
\label{sec:hhh_results_extraction}
The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable.
For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
of the observed data with the expected background distribution can be assessed. All bins
of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
methods used for this were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
and are used for all Higgs analyses in ATLAS and CMS.

For the data a likelihood function is constructed as (equation \ref{eqn:hhh_likelihood}).
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot \Sigma_j p(~\theta_j|\theta_j)
\end{equation}

Where $\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson})

\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
\end{equation}

The first term integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
in all channels and categories. $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
REFERENCE are represented by a nuisance parameter $\theta_j$. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to 1 pb, so the signal strenght modifier represents
the cross-section $\times$ branching ratio of a possible signal.

IMPROVE THIS:
The second term $p(~\theta|\theta)$ represents the pdf of the uncertainty on the nominal
value of the nuisance parameter $~\theta$.

To compare the data with the background only and signal + background hypothesis, a test
statistic $~q_{\mu}$ can be defined. This is a single 
number that is used to distinguish between the two hypotheses. The test
statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
in equation \ref{eqn:hhh_profilelikelihood}.

\begin{equation}\label{eqn:hhh_profilelikelihood}
q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}
\end{equation}

@@

Describe pdfs

The p-value for $\mu$ and for background-only ($\mu = 0$) can be determined as in equation \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}.

\begin{equation}\label{eqn:hhh_pvaluesig}
p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \Integral_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
\end{equation}

\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \Integral_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
\end{equation}

$CL_s$ is then defined as (equation \ref{eqn:hhh_cls})

\begin{equation}\label{eqn:hhh_cls}
CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}
\end{equation}

The value of $\mu$ for which $CL_s(\mu) \leq \alpha$ then gives the upper limit 
In the case of the analysis discussed in this chapter, the value of $\mu$ for which the upper 
limit on cross-section times branching ratio for the \Htohhtobbtautau process reaches $1-\alpha$ is 
said to be excluded at a confidence level of $\alpha$. Upper limits at the LHC are generally
quoted at 95\% confidence level, therefore the upper limit on cross-section times branching ratio
for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
equals 0.05. MODIFIED FREQUENTIST APPROACH.

While the distribution of $f(q_{\mu})$ can always be determined by generating toy datasets,
in the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
This formula, known as the asymptotic approximation, allows for the calculation
of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
the properties of the Asimov dataset, a dataset in which the observation in 
each bin exactly matches the background expectation.

>>>>

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{sec:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. This \Pgt-pair final states studied in this analysis
are the \etau, \mutau and \tautau channels. The results of this search are model-independent
upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, which use
combine all three channels. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered. In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau. 
This search will be summarised in this chapter, but will not constitute the main focus.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

@@

A reweighting is applied to make the pile--up distribution in \ac{MC}
match the distribution observed in data, as described in chapter OBJECT RECO.

@@

For electrons and muons, these scale factors are measured using a 
tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
The hadronic tau identification, isolation and trigger efficiencies
are measured via a similar method that makes use of
$Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.

The energy scale for hadronic taus is determined by fitting the mass of the 
hadronic tau candidate in $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
This fit is performed separately for each hadronic tau decay mode to obtain
an energy scaling that is applied to reconstructed hadronic taus matched
to generator-level hadronic tau decays in MC events.

In the \etau channel a data to \ac{MC} scale factor is applied
to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
fake rate between data and \ac{MC}. This scale factor is derived separately
for the 1-prong + 0$\pi^0$ hadronic tau decay mode, and 1-prong + at least one
$\pi^0$ decay modes by fitting the visible mass of the \Pe+$\Pgt_{h}$ pair
in $Z\rightarrow\Pgt\Pgt\rightarrow\Pe\Pgt_{h}$ events.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_signal.pdf}}
\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_ttbar.pdf}}
\end{center}
\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $GeV (left) and \ttbar background events (right) in 
the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
accuracy of the mean of the mass distribution in signal events.}%FIXME plots need to be remade as the bkg one was never released
%on the public twiki so can't have the CMS label on
\label{fig:kinfitvsmjj}
\end{figure}

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the taus. In this control region
a data-to-\ac{MC} factor is estimated and applied to the yield estimate from \ac{MC}.
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high \mT to low \mT
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is then the other-background-subtracted
data yield in the high \mT region multiplied by this extrapolation factor.
In the 2jet-2tag, a slightly different high \mT sideband of 60-120 GeV is used 
to give larger statistics for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

The \Wjets shape is taken from the \ac{MC} samples. To 
increase the statistics for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
working point for the purposes of shape estimation.
\subsection{QCD}
\label{sec:hhh_backgrounds_qcd}
A fully data-driven method is used to estimate the QCD background. Data events
passing the signal region selection cuts, but requiring the di-tau pair to be
of the same sign, are used for this. Contributions from other backgrounds are 
subtracted. Because the contribution from opposite- and same-sign QCD are
not exactly the same an OS/SS ratio of 1.06 is measured using data in which
the electron/muon isolation requirement was inverted.

@@

The shapes in all categories are taken from same-sign data with the electron/muon
isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
inverting the light lepton isolation requirements, the category definition
is loosened to obtain the shapes. For the purposes of QCD shape
estimation, jets are considered b-tagged if they pass a looser b-tagging
working point than the working point used elsewhere in the analysis.
\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shape and normalisation are
estimated using \ac{MC} samples.

\section{Systematic uncertainties}
\label{sec:hhh_uncs}
Two types of systematic uncertainties are considered: normalisation
uncertainties (which affect only the yield of a process), and shape
uncertainties (which affect both the yield and shape of a process). Section \ref{sec:hhh_results_extraction}
describes how these uncertainties are taken into account in the final result.
\subsection{Normalisation uncertainties}
\label{sec:hhh_uncs_norm}
\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during
2012 (LUMI POG CITATION?). This uncertainty is applied to all processes in which
the normalisation is estimated using MC samples.
\subsubsection*{Identification, isolation and trigger efficiencies}
A systematic uncertainty due to the uncertainty in efficiency measurements
for the leptons is derived by combining the uncertainties on these measurements
in quadrature. For electrons and muons this leads to a 2\% uncertainty, for hadronic taus a 6\% 
uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3 \% for
the \Pgt legs of the triggers. This uncertainty is applied to all processes for which
the normalisation is estimated using MC samples.
\subsubsection*{$e\rightarrow\Pgt_{h}$ and $\mu\rightarrow\Pgt_{h}$ fake rates}
The uncertainty on both the $e\rightarrow\Pgt$ fake rate measurement and the
$\mu\rightarrow\Pgt$ fake rate measurement is 30\%. The central value of the $\mu\rightarrow\Pgt$
fake rate is close to 1, which is why it is not applied, but the uncertainty is 
taken into account.
\subsubsection*{B-tag scale factors}
The b-tag scale factors are varied within their uncertainties to determine the effect
on the yields of each process. Both a b-tagging uncertainty and a fake mis-tagging
uncertainty are obtained by considering the percentage by which these backgrounds
change when the scale factors are varied within their uncertainty. The b-tagging
efficiency uncertainty amounts to 1-10\% for most processes in most categories, except for the 2jet-2tag
category where a 70\% uncertainty applies to the W background. Due to the nature
of the estimation method, where other backgrounds are subtracted from the data to 
obtain a W estimate, and the presence of large amounts of \ttbar, a 10\% change in the \ttbar
yield can vary the W yield by such large amounts.
The b mistagging rate uncertainty varies between 1-5\% for all processes in all channels.
\subsubsection*{\MET resolution and response}
Uncertainties on the \MET resolution and response are estimated by varying
the recoil correction parameters within their estimated uncertainties. This 
leads to a 1-10\% uncertainty (depending on category and process)
\subsubsection*{Background normalisation}
\begin{itemize}
\item \Ztautau : the normalisation of the embedded samples attracts a 3.3\% uncertainty, which is derived
from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples. In addition an uncertainty of 5-6\% for extrapolation from the inclusive selection to the category selection is applied.
\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\%
\item \ttbar: the uncertainty on the \ttbar cross section is 10\%
\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
\item \Wjets: As the \Wjets yield is estimated from a high \mT sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty range sfrom 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
\item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio. This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category.
\end{itemize}
\subsection{Shape uncertainties}
\label{sec:hhh_uncerts_shape}
\subsubsection*{Tau energy scale}
The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty. As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.
\subsubsection*{Jet energy scale}
The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the (\pT and $\eta$ dependent) uncertainty. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty 
\section{\texorpdfstring{Overview of \AtoZhtolltautau}{Overview of A->Zh->lltautau}}
\label{sec:hhh_azh}
In this section a summary of the \AtoZhtolltautau analysis, which is combined with the 
analysis described so far for the purposes of model interpretations, is given.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
\caption{The 95\% confidence level expected (dashed) and observed (solid)
upper limits on the $\sigma \times BR$ for the \AtoZhtolltautau process.
The green and yellow bands indicate the $\pm 1 \sigma $ and $2\sigma$
expectations \cite{CMS-HIG-14-034}.}
\label{fig:AZhUpperLimits}
\end{center}
\end{figure}

More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
For the purposes of combining the results with the \Htohhtobbtautau search,
some of these are correlated between the two analyses.
This applies to the
luminosity uncertainty and the uncertainties on b-tagging efficiency
and light jet mistagging rate.

\section{Results}
\label{sec:hhh_results}
\subsection{Signal extraction}
\label{sec:hhh_results_extraction}
The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable.
For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
of the observed data with the expected background distribution can be assessed. All bins
of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
methods used for this were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
and are used for all Higgs analyses in ATLAS and CMS.

For the data a likelihood function is constructed as (equation \ref{eqn:hhh_likelihood}).
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta)
\end{equation}

Where $\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson})
\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
\end{equation}

The first term integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
in all channels and categories. $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
\ref{sec:hhh_uncs} are each represented by a nuisance parameter $\theta_j$. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to 1 pb, so the signal strenght modifier represents
the cross-section $\times$ branching ratio of a possible signal.

The second term $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section\ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainy. Normalisation uncertainties are applied as log-normal constraints.
For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
yields do not become negative. Shape uncertainties are accounted for using a vertical template morphing
technique. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter $\lambda$ is added to the likelihood model as a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in event statistics for shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template are allowed to float within their statistical uncertainty, independent of the other bins. These
variations are controlled by log-normal constraints in the likelihood function.

To compare the data with the background only and signal + background hypotheses, a test
statistic $q_{\mu}$ can be defined. This is a single 
number that is used to distinguish between the two hypotheses. The test
statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
in equation \ref{eqn:hhh_profilelikelihood}.
\begin{equation}\label{eqn:hhh_profilelikelihood}
q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}
\end{equation}

@@

The probability of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
and assuming the background-only hypothesis, is given in equations \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}, respectively.

\begin{equation}\label{eqn:hhh_pvaluesig}
p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
\end{equation}

\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
\end{equation}

Where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability denstiy functions of $q_{\mu}$ under
the signal+background and background-only hypotheses.

Using this, $CL_s$ is defined as (equation \ref{eqn:hhh_cls})
\begin{equation}\label{eqn:hhh_cls}
CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}
\end{equation}

The value of $\mu$ for which $CL_s(\mu) \leq \alpha$ then gives the upper limit 
In the case of the analysis discussed in this chapter, the value of $\mu$ for which the upper 
limit on cross-section times branching ratio for the \Htohhtobbtautau process reaches $1-\alpha$ is 
said to be excluded at a confidence level of $\alpha$. Upper limits at the LHC are generally
quoted at 95\% confidence level. %, therefore the upper limit on cross-section times branching ratio
%for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
%equals 0.05. The use of $CL_s$ to set
The use of $CL_s$ to set exclusion limits is referred to as the modified frequentist approach\cite{CLS}.

The distributions $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu}|0,\hat{\theta_0})$ are determined
using toy MC datasets. These datasets are generated from the sum of signal+background or background only expectation respectively. 
For each toy dataset the nuisance parameters fixed to the best-fit values found in the fit to observed data are taken as a starting
point, and the effect of systematic uncertainties is then taken into account by varying the nuisance parameters within
their uncertainty. The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal+background or background only)
can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.

This method of generating toy MC datasets is computationally intensive.
In the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
This formula, known as the asymptotic approximation, allows for the calculation
of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
the properties of the Asimov dataset, a dataset in which the observation in 
each bin exactly matches the predictions of the model. This method is used for the analysis
described in this chapter, removing the need to generate toy datasets.
